White Dwarf Mergers on Adaptive Meshes\\ II. Nuclear Reactions

### 2018-01-28 papers/wdmerger_II/paper.tex
Add release information
Remove specificity about the time of the restart

We implement the white dwarf collision problem in \castro\ in the \wdmerger\ problem
directory. We prepare the domain in the way most previous papers have done so:
the white dwarf centers of mass are initially separated by a distance of four times
the (secondary) white dwarf radius. Note that the radius of the white dwarf, and
consequently the initial distance, depends on the equation of state used, and this
can vary somewhat depending on the relevant physics used, such as Coulomb corrections
in the Helmholtz equation of state. However, the results do not really depend on the
exact initial distance as long as there is enough time for the WDs to distort in
response to tidal forces as they approach. Their initial velocity is that of
two point-masses in free-fall towards each other coming in from infinity, such that
the contact point is at the origin, and they approach each other along a coordinate axis.
In this paper we focus only on head-on collisions of two 0.64 $\msolar$ white dwarfs
composed of equal parts carbon and oxygen by mass, at an initially uniform temperature
of $T = 10^7$ K. This choice is for comparison to earlier studies; the code does have
the ability to vary the impact parameter of the collision and the mass and composition
of the WDs.

@@

To answer these questions we performed a series of simulations at varying base
resolutions, augmented with additional runs with AMR. In each case we ran the
simulation to the point at which unstable burning was approached:
$\tau_{s} / \tau_{e} = 10^{-6}$. Then we stopped
the run and created a checkpoint. Starting from that checkpoint, we did a simulation
at varying levels of refinement based on the unstable burning criterion. We will refer
to the refinement through the refinement factor, $r$. This factor is the jump in
resolution between the coarse grid and the finest grid. The uniform base grid case is $r = 1$.
Meanwhile, $r = 16$ means a uniform coarse grid plus two levels of 4x refinement.

>>>>

We implement the white dwarf collision problem in \castro\footnote{The main results
in this paper were generated using the 17.12 releases of \castro, \amrex, and
\microphysics.} in the \wdmerger\ problem
directory. We prepare the domain in the way most previous papers have done so:
the white dwarf centers of mass are initially separated by a distance of four times
the (secondary) white dwarf radius. Note that the radius of the white dwarf, and
consequently the initial distance, depends on the equation of state used, and this
can vary somewhat depending on the relevant physics used, such as Coulomb corrections
in the Helmholtz equation of state. However, the results do not really depend on the
exact initial distance as long as there is enough time for the WDs to distort in
response to tidal forces as they approach. Their initial velocity is that of
two point-masses in free-fall towards each other coming in from infinity, such that
the contact point is at the origin, and they approach each other along a coordinate axis.
In this paper we focus only on head-on collisions of two 0.64 $\msolar$ white dwarfs
composed of equal parts carbon and oxygen by mass, at an initially uniform temperature
of $T = 10^7$ K. This choice is for comparison to earlier studies; the code does have
the ability to vary the impact parameter of the collision and the mass and composition
of the WDs.

@@

To answer these questions we performed a series of simulations at varying base
resolutions, augmented with additional runs with AMR. In each case we ran the
simulation to a point just after the burning started, but before a detonation
had occurred. Then we stopped
the run and created a checkpoint. Starting from that checkpoint, we did a simulation
at varying levels of refinement based on the unstable burning criterion. We will refer
to the refinement through the refinement factor, $r$. This factor is the jump in
resolution between the coarse grid and the finest grid. The uniform base grid case is $r = 1$.
Meanwhile, $r = 16$ means a uniform coarse grid plus two levels of 4x refinement.
